---
title: "Offence Principles"
---

```{r,setup}
#| echo: false
#| message: false
#| warning: false

library(ggulti)
library(tidyverse)
library(patchwork)
library(gganimate)

hu_pal <- c("#134072", "#036d3f", "#edb945", "#d63c3c", "#6d6e6d")

pitch <- ggpitch(type = "full", endzone_fill = hu_pal[3],colour = hu_pal[5])

pitch_a <- ggpitch(type = "half_attack", endzone_fill = hu_pal[5],colour = hu_pal[5])

pitch_d <- ggpitch(type = "half_defend", endzone_fill = hu_pal[5],colour = hu_pal[5])

ggulti_plot_values$obj_cols["Offense"] <- hu_pal[1]
ggulti_plot_values$obj_cols["Defense"] <- hu_pal[2]
ggulti_plot_values$obj_sizes["Disc"] <- 3
ggulti_plot_values$obj_sizes["Offense"] <- 3.5
ggulti_plot_values$obj_sizes["Defense"] <- 3.5


ppv <- ggulti_plot_values

```

## Philosophy 

Hillhead’s offence is built on disciplined possession and positive, attacking play that prioritises moving the disc into valuable spaces on the field. Isolated cutters create opportunities for big gains and break-side continuation. This is complemented by handler-driven flow that keeps the disc moving to stretch the defence and open up new attacking angles. This strategy emphasises intelligent movement, anticipation of play and strong communication, ensuring the disc stays safely in motion until a high-value opening presents itself.

## Structure and spacing

#### Identify active spaces

**Active spaces** are the areas on the field where we typically look to make low risk, positive passes. Often, but not always, in this order of preference:

- <span style="color: #464FB1;">Deep space:</span> To score
- <span style="color: #008293;">Break space:</span> To open up break-side continuation
- <span style="color: #D15609;">Throwing lane:</span> Easy up-field pass
- <span style="color: #DB127A;">Swing space:</span> To open up bigger active spaces

```{r, structure}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

players <- list(
  pitch_object(label = "Thrower", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:3),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 1, frame = 1:3),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 1, frame = 1:3),
  pitch_object(label = "A", x = c(5,14,14),
  y = c(44,41,80), show = F, alpha = 1, frame = 1:3),
  pitch_object(label = "B", x = c(16,15,5),
  y = c(44,70,50), show = F, alpha = 1, frame = 1:3),
  pitch_object(label = "C", x = c(35), frame = 1:3,
  y = c(42), show = F, alpha = 1,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:3,
  y = c(46), show = F, alpha = 1,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),alpha = 1,show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),alpha = 1,show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),alpha = 1,show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),alpha = 1,show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),alpha = 1,show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),alpha = 1,show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),alpha = 1,show = F)
)

arrows = ggulti::object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))

base <- list(
  geom_rect(aes(xmin=8, xmax=20, ymin=28, ymax=48), fill="#008293", alpha=0.4),
  geom_rect(aes(xmin=0, xmax=10, ymin=22, ymax=70), fill="#D15609", alpha=0.4),
  geom_rect(aes(xmin=3, xmax=29, ymin=9, ymax=21), fill="#DB127A", alpha=0.4),
  geom_rect(aes(xmin=0, xmax=30, ymin=74, ymax=100), fill="#464FB1", alpha=0.4),
  geom_text(aes(x=16, y=15, label="Swing Space"), color="#DB127A", size=3),
  geom_text(aes(x=5, y=33, label="Throwing\nLane"), color="#D15609", size=3),
  geom_text(aes(x=14, y=38, label="Break Space"), color="#008293", size=3),
  geom_text(aes(x=15, y=87, label="Deep Space"), color="#464FB1", size=3)
)

plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T, base = base) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  theme_void() +
  coord_fixed(ratio = 0.5)

```

#### Isolate active cutters

Ideally, we want 1 or 2 active cutters in front of the disc, attacking the up-field active spaces. Other players on the field should give them space and time to cut. 

#### Isolate the reset handler

The reset handler provides support when there are no up-field options. They offer positive up-field cuts or a route to move the disc laterally through the swing space. Other players should not encroach on the reset or cut into their space. Give them room a swing pass or to cut up the line. 

#### Continuation cutters / handlers

Continuation cutters and handlers should stay out of active spaces. Their job is to create space while anticipating their turn to become active when the disc moves or an active player clears out. You need to be disciplined in creating space and trust the active players to do their job.

You also need to look like a threat. If you are too static then your defender will be able to poach the active spaces. Keep moving, put in a few fake cuts, and be ready to attack if an opportunity arises.

#### **Keep the active spaces clear**

- Leave space to throw into
- Leave space for active cutters to attack
- Active cutters cannot hang around in attacking spaces - clear quickly!

## Cutting and movement

#### **Active cutters**

Active cutters are the players in front of the disc trying to make big up-field gains. When you are active, you need to cut aggressively and avoid clogging the active spaces.

Use big cutting shapes that maximise gains and make it obvious to the thrower which spaces you are attacking. You can still change speed and direction to lose your mark but avoid dancing  when attacking active space. Actively engage with the thrower via vocal communication, pointing, eye contact etc. The three cutting shapes we use the most are outlined below.

#### Going deep

Always cut to score if the throw is on. Your defender has to respect this, even if you don’t get the disc it may open up a big space to cut under.

- Start from **shallow** to allow the disc to be thrown into space
- Stay **wide** of the throwing lane when cutting
  - Keep the lane clear for throws
  - Allows you to see the disc in flight
  - Adjust when the disc is in flight
- Clear or cut under if you don’t get the disc

```{r, deep}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

players <- list(
  pitch_object(label = "Thrower", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(5,12),
  y = c(44,41), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(16,15),
  y = c(44,70), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "C", x = c(35), frame = 1:2,
  y = c(42), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(46), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=10, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) + 
  ggtitle("Break side") +
  theme(plot.title = element_text(size = 10))


### Open side

players <- list(
  pitch_object(label = "H1", x = c(15),
  y = c(15), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "H2", x = c(18.5),
  y = c(23), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "H3", x = c(35),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(2),
  y = c(41), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(8),
  y = c(41,60), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "C", x = c(29), frame = 1:2,
  y = c(41), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(41), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(-0.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[4]], xjust = c(1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1), yjust = c(-2.5),show = F),
                defender(players[[6]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-1.5), yjust = c(1),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 17.5,y = 23.5,show = F,alpha = 1))

p2 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = c(12,22), linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=22, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Central") +
  theme(plot.title = element_text(size = 10))

p1 + p2 + plot_layout(guides = "collect")
```


#### Coming under

If you threaten deep, you will find that space opens up for you underneath. Aim for big gains and clear early if the throw isn’t on.  

- Cut under at an **angle** to the throwing lane
  - Larger margin of error on the throw
  - Less time spent clogging the throwing lane
  - Better continuation options after a catch
- **Clear the lane early** if you don’t get the disc
  - Small gains on the open side are not very valuable*
  - Clear space for the next cut
  
*Unless it’s a high stall or the only option to get the disc moving.

```{r, under}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

players <- list(
  pitch_object(label = "Thrower", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(15,15),
  y = c(41,50), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(15,3),
  y = c(60,41), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "C", x = c(35), frame = 1:2,
  y = c(42), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(46), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))


p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=10, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Break side") +
  theme(plot.title = element_text(size = 10))


## central
players <- list(
  pitch_object(label = "H1", x = c(15),
  y = c(15), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "H2", x = c(18.5),
  y = c(23), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "H3", x = c(35),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(2),
  y = c(41), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(8),
  y = c(41), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "C", x = c(29,16), frame = 1:2,
  y = c(60,42), show = F, alpha = 1,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(41), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(-0.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[4]], xjust = c(1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[7]], xjust = c(-1.5), yjust = c(1),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 17.5,y = 23.5,show = F,alpha = 1))


p2 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = c(12,22), linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=22, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Central") +
  theme(plot.title = element_text(size = 10))

p1 + p2 + plot_layout(guides = "collect")

```

#### Slash to the breakside

The slash cut is a powerful move that can open up the break-side and create opportunities for easy continuation passes. 

- Make a **lateral** cut across the throwing lane to the break side
  - Attack the break-side
  - Clear the lane for throws to other cuts
- When possible, start **wide** of the lane, to create a big <span style="color: #008293;">throwing window</span> for the inside throw
  - The thrower can throw into space
  - The thrower doesn't need to take on the force
- **Clear** to the inactive side or attack deep if you don’t get the disc


```{r, slash}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

base <- list(
  geom_rect(aes(xmin=5, xmax=10, ymin=27, ymax=40), fill="#008293", alpha=0.4)
)

players <- list(
  pitch_object(label = "Thrower", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(5,12),
  y = c(41,39), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "B", x = c(15),
  y = c(41,55), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "C", x = c(35), frame = 1:2,
  y = c(42), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(46), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T, base = base) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=10, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Clearing the lane") +
  theme(plot.title = element_text(size = 10))

## central

base <- list(
  geom_rect(aes(xmin=12, xmax=22, ymin=27, ymax=40), fill="#008293", alpha=0.4),
  geom_text(aes(x=17, y=33.5, label="Throwing\nwindow"), color="#008293", size=3)
)

players <- list(
  pitch_object(label = "H1", x = c(15),
  y = c(15), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "H2", x = c(18.5),
  y = c(23), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "H3", x = c(35),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(2),
  y = c(41), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(10,26),
  y = c(41), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "C", x = c(29), frame = 1:2,
  y = c(41,55), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(41), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(-0.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[4]], xjust = c(1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[7]], xjust = c(-1.5), yjust = c(1),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 17.5,y = 23.5,show = F,alpha = 1))

p2 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T, base = base) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = c(12,22), linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=22, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Wide of the lane") +
  theme(plot.title = element_text(size = 10))

p1 + p2 + plot_layout(guides = "collect")

```

You can link an under cut to a slash cut. Finish your under cut **wide** on the open side to create a big <span style="color: #008293;">throwing window</span> for your slash cut.

```{r, slash2}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

## under cut to slash

base <- list(
  geom_rect(aes(xmin=12, xmax=22, ymin=27, ymax=40), fill="#008293", alpha=0.4),
  geom_text(aes(x=17, y=33.5, label="Throwing\nwindow"), color="#008293", size=3)
)

players <- list(
  pitch_object(label = "H1", x = c(15),
  y = c(15), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "H2", x = c(18.5),
  y = c(23), show = F, alpha = 1, frame = 1:3),
  pitch_object(label = "H3", x = c(35),
  y = c(23), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "A", x = c(2),
  y = c(41), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "B", x = c(28),
  y = c(50), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "C", x = c(26,12,26), frame = 1:3,
  y = c(70,41,41), show = F, alpha = 1,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:3,
  y = c(41), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(-0.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[4]], xjust = c(1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[7]], xjust = c(-1.5), yjust = c(1),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 17.5,y = 23.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T, base = base) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = c(12,22), linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=22, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Big window") +
  theme(plot.title = element_text(size = 10))

## under cut to slash small

base <- list(
  geom_rect(aes(xmin=18, xmax=22, ymin=27, ymax=40), fill="#008293", alpha=0.4)
)

players <- list(
  pitch_object(label = "H1", x = c(15),
  y = c(15), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "H2", x = c(18.5),
  y = c(23), show = F, alpha = 1, frame = 1:3),
  pitch_object(label = "H3", x = c(35),
  y = c(23), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "A", x = c(2),
  y = c(41), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "B", x = c(28),
  y = c(50), show = F, alpha = 0.2, frame = 1:3),
  pitch_object(label = "C", x = c(26,18,26), frame = 1:3,
  y = c(70,41,41), show = F, alpha = 1,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:3,
  y = c(41), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(-0.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[4]], xjust = c(1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[7]], xjust = c(-1.5), yjust = c(1),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 17.5,y = 23.5,show = F,alpha = 1))

p2 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T, base = base) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=10, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Small window") +
  theme(plot.title = element_text(size = 10))

p2 + p1 + plot_layout(guides = "collect")

```

#### Cutting sequences

The cutting shapes above can be linked together in a powerful cutting **sequence**. For example, you can start with a deep cut on the break side, come under on an angle to the lane, slash to the break-side, then go deep again. By linking cuts into sequences you give yourself multiple chances to get open for the thrower. Each change of direction is an opportunity to lose your defender, so turn *sharply*, *explosively* and use *misdirection* to your advantage.

```{r, sequence}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

players <- list(
  pitch_object(label = "Thrower", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:4),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 0.1, frame = 1:4),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 0.1, frame = 1:4),
  pitch_object(label = "A", x = c(5),
  y = c(41), show = T, alpha = 0.1, frame = 1:4),
  pitch_object(label = "B", x = c(15,15,5,15),
  y = c(41,70,42,41), show = T, alpha = 1, frame = 1:4),
  pitch_object(label = "C", x = c(35), frame = 1:4,
  y = c(42), show = F, alpha = 0.1,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:4,
  y = c(46), show = F, alpha = 0.1,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5,1.5,-1.5,-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4, show_all = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=10, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8, show_all = T) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Sideline cutting sequence") +
  theme(plot.title = element_text(size = 10))

p1
#p1 + 
#transition_states(states = factor(frame, levels = 1:4), transition_length = 0.5, state_length = 0.5, wrap=F) +
#  enter_fade()

```

Some offence structures use multiple active cutters. In this case, you also need to think about the **timing** of your cutting sequence:

  - Cut in different moments and directions to create multiple options for the thrower
  - Cut to **free up space** for your teammate to attack
  - **Delay** your cut or change of direction until your teammate has cleared the throwing lane and the space you want to attack

In the example below, cutter **B** starts wide to create a throwing window for a slash cut from **A**. Because **A** starts in the throwing lane, **B** drifts up-field but delays the attacking cut deep until A has cleared the lane.

```{r, active pair}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

players <- list(
  pitch_object(label = "Thrower", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:5),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 0.2, frame = 1:5),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 0.2, frame = 1:5),
  pitch_object(label = "A", x = c(5,12,12,12,5),
  y = c(41,39,39,60,41), show = F, alpha = 1, frame = 1:5),
  pitch_object(label = "B", x = c(16,15,13,5,12),
  y = c(41,48,70,41,39), show = F, alpha = 1, frame = 1:5),
  pitch_object(label = "C", x = c(35), frame = 1:5,
  y = c(42), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:5,
  y = c(46), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4, show_all = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=10, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Cutting as an active pair") +
  theme(plot.title = element_text(size = 10))

p1
#p1 + 
#transition_states(states = factor(frame, levels = 1:5), transition_length = 0.5, state_length = 0.5, wrap=F) +
#  enter_fade()
```


The cutting shapes above are a good starting point for learning how to cut as they are often the most effective options for attacking the active spaces. However, they are not the only options and it is important to react to the spaces on the field and the positions of defenders. Be **creative** and **adapt** your cutting accordingly. 

Sometimes it gets messy; the defence clogs spaces; the thrower is under pressure; your teammates are running into each other; and it's impossible to find the right cut. Be **patient**, stick to good cutting principles, work hard to create space and find the best positions to launch an attacking cut.

#### **Setting up a cut**

Good cutting isn’t just about speed and effort, it also requires good positioning, timing and intention. The best cutters don’t just run into open space, they create that space first. This preparatory movement is what we refer to as **setting up**. 

A good set up allows you to: 

  - Get **separation** from your defender
  - Launch your attack from a strong **position** (think about the ideal launch points for the cutting shapes above)
  - Launch your attack at the right **time**
  
Setting up can take many forms depending on the situation. It might be as simple as positioning yourself between your defender and the space you want to attack, or drifting into areas that open up better cutting angles. At other times, it requires more work, aggressively clearing space to reposition yourself, or explosively changing direction to shake your mark.

**Active** cutters have very little time to set up, usually one or two quick movements before they have to attack space or clear out. This is especially true when starting from a static position or when the disc moves and the active space changes. 

**Continuation** cutters have more opportunity to prepare. By using areas outside of the active space and anticipating the flow of play, they can launch attacking active cuts at the right time and from a strong position.

#### Get separation from your defender

  - Use your body to **seal** your defender off from the space you want to attack
  - Use **change of speed** and **change of direction** to get separation
  - Get your defender **off balance** or committing in one direction, then attack against their momentum

#### Launch your attack from a strong position:

  - Find the right **launch point** for your attacking cut e.g
    - Going deep: Shallow and wide of the lane
    - Coming under: Deep and wide of the lane
    - Slash: Open side and wide of the lane
  - Find <span style="color: #d63c3c;">apex points:</span> Positions with multiple attacking options that are difficult for your defender to cover e.g
    - A deep strike or a big gain under
    - An open under or a big break side window
    - A handler strike up the line or attacking the swing space

```{r, apex_points}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600  

players <- list(
  pitch_object(label = "H1", x = c(10),
  y = c(21), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "H2", x = c(18.5,15),
  y = c(23,24), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "H3", x = c(35),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(7.5,5),
  y = c(50,41), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "B", x = c(18,15),
  y = c(44,46), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "C", x = c(35), frame = 1:2,
  y = c(43), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(41), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(2.5),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[7]], xjust = c(-1.5), yjust = c(1),show = F)
)

arrows = object_paths(players)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 9,y = 21.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_curve(aes(x=5, y=41, xend=3, yend=33), color="#d63c3c", linewidth=0.8, arrow=arrow(length=unit(0.2,"cm")),curvature=0) +
    geom_curve(aes(x=5, y=41, xend=10, yend=41), color="#d63c3c", linewidth=0.8, arrow=arrow(length=unit(0.2,"cm")),curvature=0) +
    geom_curve(aes(x=15, y=46, xend=15, yend=60), color="#d63c3c", linewidth=0.8, arrow=arrow(length=unit(0.2,"cm")),curvature=0) +
    geom_curve(aes(x=15, y=46, xend=10, yend=38), color="#d63c3c", linewidth=0.8, arrow=arrow(length=unit(0.2,"cm")),curvature=0) +
    geom_curve(aes(x=15, y=24, xend=10, yend=31), color="#d63c3c", linewidth=0.8, arrow=arrow(length=unit(0.2,"cm")),curvature=0) +
    geom_curve(aes(x=15, y=24, xend=18, yend=21), color="#d63c3c", linewidth=0.8, arrow=arrow(length=unit(0.2,"cm")),curvature=0) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  ggtitle("Apex points") +
  theme(plot.title = element_text(size = 10))

p1
```

#### Launch your attack at the right time: 

Timing your attacking cut is crucial for getting open and maximising the space to throw into. Use these cues to time your cut:

  - As a receiver **catches** the disc
    - Be the immediate continuation option for a thrower. Time your cut to be open and attacking space as the receiver is ready to throw:
      - Going too early shrinks the throwing window and makes the throw more difficult or less advantageous
      - Going too late stifles flow as there is no immediate option for quick continuation, allowing the defence to recover
  - As a thrower **fakes**
    - If you aren't in a position for immediate continuation, try to set yourself up for the thrower’s second look. 
    - Anticipate the thrower faking to an active cut and looking for the next option
    - Good fakes can cause defenders to over-commit and open up new spaces to attack
  - As an active cutter **clears**
    - Ensures the active space is free to attack
    - Gives an immediate backup option for the thrower 
  
#### Keep the active spaces clear 

  - Active cutters
    - Use a quick set up to get free or create a better cutting angle
    - Don’t clog the active space with small movements or by being indecisive about your cut. If you are in the active space, you need to be attacking it or clearing out*
  - Continuation cutters
    - Set up a cut without interfering with active cutters/spaces
    - Pull out of an attacking cut early if it’s not a good option 
  
*The exception here is when you are unmarked e.g in a zone or a poach. If you are wide open, it is often best to just stay still and let the thrower hit you.

## Throwing to active spaces

The attacking nature of our offence is built into the system and the active spaces we use on the field. Our cutters are responsible for creating these spaces through disciplined cutting, spacing and timing. This reduces pressure on throwers to take risks or force the disc through small windows. While there is room for creativity, there is no need to be risky or overly-aggressive. Instead, the focus is on accuracy, timing, and leading receivers into good continuation options.

Here are some key pointers for throwing to our preferred cutting shapes:

#### Throwing to deep cuts

  - Throw **early** and into space for the receiver to run down at speed
  - **Shape** the throw into the receiver’s path and away from defenders
  - Keep the disc in the receiver’s **vision**
    - Avoid throwing over their head

```{r, deep_throw}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600 

players <- list(
  pitch_object(label = "H1", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(18),
  y = c(41), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(12,11),
  y = c(41,80), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "C", x = c(35), frame = 1:2,
  y = c(42), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(46), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),show = F)
)

throws <- throw(players,"t1",from = "H1", to = "B",arrow_shape = "bhrc",show=F,frame = 1:2,throw_frame = 2)
cuts <- object_paths(players)
arrows = list(cuts,throws)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  theme_void() +
  coord_fixed(ratio = 0.5) + 
  ggtitle("Deep throw") +
  theme(plot.title = element_text(size = 10))

p1
```

#### Throwing to under cuts

When throwing to under cuts, the key is to throw into the space the receiver is attacking rather than directly at them. This allows the receiver to adjust if the throw is slightly off target.  

```{r, under_throw}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

players <- list(
  pitch_object(label = "H1", x = c(5),
  y = c(21), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "Reset", x = c(20),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "CH", x = c(35),
  y = c(31), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(15,15),
  y = c(41,50), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(15,4),
  y = c(60,41), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "C", x = c(35), frame = 1:2,
  y = c(42), show = F, alpha = 0.2,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(46), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(-1.5), yjust = c(3),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[4]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(-1.5),show = F),
                defender(players[[7]], xjust = c(-2.5), yjust = c(-1.5),show = F)
)

throws <- throw(players,"t1",from = "H1", to = "B",show=F,frame = 1:2,throw_frame = 2)
cuts <- object_paths(players)
arrows = list(cuts,throws)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 4,y = 21.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = 10, linetype = "dashed", color = "#D15609", alpha = 0.5) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Throwing to an under") +
  theme(plot.title = element_text(size = 10))

p1
```

#### Throwing to the break side

Why do we want to throw to the break side?

  - Catches have **less defensive pressure** as the receiver's defender is on the wrong side
  - To **escape** the areas where the defence is most concentrated and cloggingg space
  - To create opportunities for immediate break-side **continuation**
    - While the defence is on the wrong side

Because big gains are made on the continuation pass, the break side throw should be low-risk and set the receiver up for the next throw. 

  - Throw into **big windows**
    - Avoid squeezing the disc into tight spaces or between defenders
  - Try to **lead the receiver** into good break side continuation options

When throwing to the slash cut there are two main options:

  - **A**: Throw up the lane into the cutter's chest and allow their momentum to carry them to the break-side 
    - Easier option as still an open-side throw but leads the receiver to the break-side
  - **B**: Take on the force and float the disc into the break-side for the receiver to run onto
    - Need to break the force but can lead the cutter further to the break-side and slightly up-field, creating better angles and more time for continuation passes

```{r, break_throws}
#| echo: false
#| message: false
#| warning: false
#| fig-height: 4
#| fig-width: 7
#| fig-dpi: 600

players <- list(
  pitch_object(label = "H1", x = c(15),
  y = c(15), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "H2", x = c(18.5),
  y = c(23), show = F, alpha = 1, frame = 1:2),
  pitch_object(label = "H3", x = c(35),
  y = c(23), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "A", x = c(2),
  y = c(41), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "B", x = c(28),
  y = c(70), show = F, alpha = 0.2, frame = 1:2),
  pitch_object(label = "C", x = c(11,17.5), frame = 1:2,
  y = c(41,41), show = F, alpha = 1,label_pos = "up"),
  pitch_object(label = "D", x = c(35), frame = 1:2,
  y = c(41), show = F, alpha = 0.2,label_pos = "up")
)

defense <- list(defender(players[[1]], xjust = c(-0.5), yjust = c(2.5),show = F),
                defender(players[[2]], xjust = c(1.5), yjust = c(2.5),show = F),
                defender(players[[3]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[4]], xjust = c(1.5), yjust = c(-1.5),show = F),
                defender(players[[5]], xjust = c(-1.5), yjust = c(-1.5),show = F),
                defender(players[[6]], xjust = c(-2.5), yjust = c(1.5),show = F),
                defender(players[[7]], xjust = c(-1.5), yjust = c(1),show = F)
)

throws <- list(
  throw(players,"A",from = "H2", to = "C",show=T,frame = 1:2,throw_frame = 2, label_pos = "end_up"),
  throw(players,"B",from = "H2", to = "space", space_x = 25, space_y = 42, show=T, arrow_shape = "bhio", frame = 1:2,throw_frame = 2, label_pos = "end_up"),
  throw(players,"C",from = "H2", to = "space", space_x = 25, space_y = 42, show=F, arrow_shape = "bhrc", frame = 1:2,throw_frame = 2)
)
cuts <- object_paths(players)
arrows = list(cuts,throws)

objects <- list(players,defense,static_objects(object = "Disc",label="Disc",x = 17.5,y = 23.5,show = F,alpha = 1))

p1 <- plot_play(pitch = pitch,object_list = objects, arrow_list = arrows, pv = ppv,default_obj_size = 4,keep_arrows = T) +
  guides(colour = guide_legend(override.aes = list(shape = 16, linetype = 0, size = 3))) +  
  geom_vline(xintercept = c(12,22), linetype = "dashed", color = "#D15609", alpha = 0.5) +
  geom_text(aes(x=22, y=70, label="Throwing Lane"), color="#D15609", size=2.5, angle = 90, vjust = 1.5, alpha = 0.8) +
  theme_void() +
  coord_fixed(ratio = 0.5) +
  labs(title = "Slash cut to break-side") +
  theme(plot.title = element_text(size = 10))
p1
```

## Continuation and flow

Continuation and flow are the principles that keep our offence moving without letting the defence settle.

**Continuation** is the act of immediately following up a completed pass with another well-timed throw, taking advantage of the space and momentum just created,

**Flow** is the overall movement of the disc and players in a connected, rhythmic way that maintains offensive momentum, opens up new angles, and keeps the defence on its toes.
  
When a pass is made, try to keep the disc moving quickly and safely to maintain momentum. This might be a quick continuation throw to a well timed cut or some small-ball movement with players in close proximity. This keeps the offence flowing, creates space up-field and exploits gaps while the defence is still recovering.

  - **Catch and move into a throwing motion**
    - Ready to hit a quick continuation pass if it’s on
    - OR: Throw a believable fake to shift the defence and open up another space to attack
  - **Hit the first open pass**
    - Keep the disc moving and the offence flowing
    - Don't look off an open throw just because it's not the most exciting option
      - You might not get a better option
      - Move the disc and encourage better cutting options in future
    - Don’t wait for cuts to appear if nothing is happening up-field
      - Engage your reset
  - **Hit the pass in front of you**
    - Look for immediate continuation options within your field of vision
    - Prioritise passing to players moving in the direction of attack
      - Use throw and go moves and give the disc to advancing handlers
  - **Find power positions**
    - Power positions are catching positions where the receiver’s momentum allows them to throw quick continuation throws without a force
    - Often generated from up-the-line cuts, leading break throws and big swings
    - Cutters should learn to recognise the patterns that lead to power positions and set up an attacking cut!
  - **Attack the break-side**
    - Throws to the break-side open up big continuation spaces
    - Try to move the disc quickly after a break throw to take advantage

#### When flow breaks down

When flow breaks down, get back into **structure** quickly. Position your reset and active cutters and look to attack the active spaces or engage the reset.

Be **patient**. Keeping possession is the key to a successful offence. Moving the disc quickly and taking on throws to big spaces should not be confused with taking high risk options. We are happy to **maintain possession** until a good attacking opportunity presents itself.

## Handler Movement

#### **Resets**

The reset handler supports the thrower by supplying a backup option when there are no viable up-field passes and also provides a route to attack the pitch laterally through the swing space. Resets should be aggressive, positive moves that advance the disc to a stronger area of the pitch or open up new active spaces.

##### Engage the reset early

Don’t let the defence settle in one position for too long. If there are no good up-field options, engage your reset and move the disc. It is important to engage your reset early in the stall count to give time for them to cut or clear for another option.

  - By stall 4: In the centre of the field
  - By stall 2: On or near a sideline
  - Immediately: If there are no up-field options developing

#### The handler space

Early in the stall, the resets job is to get into a good position, anticipate play and prepare to become active when they are engaged by the thrower.

The reset can use the **handler space** to set up without interfering with up-field options. It is important for other players to keep this space free for the reset. Think about the space between the disc and the reset as a **life-line** that cannot be severed.

Once the reset becomes active, they have priority and other players should give them room to attack up-the-line or into the swing space. The handler space effectively expands to include these active spaces. Up-field cutters can continue to cut and provide options, but avoid clogging the space in the reset’s path.

FIGURE

#### Reset positioning and movement

Central channel:
Position = 45 degrees on the open side
Active cutting options
Plinko cut 
Breakside continuation
Upfield cut
Power-position continuation
Give-go (if poached)
Power-position continuation
Clearing out
If you commit to a cut and don’t get the disc, clear the reset space
Avoid dancing in small spaces. It is better to clear for another cutter.
 
Fig 8: Reset - centre

Sideline and outer channels:
Position = Level or slightly upfield, start towards the centre of the field to give room to get free
Active cutting options
Attack up the line as first option
Power-position continuation
Otherwise, hit the swing pass
Lead the reset into swing space continuation
Clearing out
If you commit to the up the line cut and don’t get the disc, clear out of the handler space
If you don’t get the swing pass, drive up the line, then clear out

Fig 8: Reset - outer channels

Thrower/reset communication
Resets can be time pressured and sometimes have limited space to work with. It is important that the thrower and receiver communicate.

Make eye contact, or physically turn towards your reset handler to engage them in play
Reset: Put your hand out into the swing space if you are looking for a lateral pass
Thrower: Fake at the reset to tell them to drive upfield

Reset continuation passes

Good reset passes create great continuation options:

Swing pass -> Continue the swing across and upfield
Keep the swing space clear and time cuts for maximum gains
Up the line pass -> Power position huck
Attack deep!
The third handler
The role of the third handler is very similar to a continuation cutter, except that they are providing support for the reset. They should be ready to offer good continuation cuts around the swing space, or provide a secondary reset cut if the original reset clears out. Positioning and cutting options can vary depending on the offence structure but the principles remain the same: Give the reset time and space to get free, anticipate play and set up your attacking move, keep the swing space clear for throws.

Fig 9: Standard swing to the break side, third handler opening up swing space



#### Throwing to the swing space

Throw leading passes for swing space continuation

#### Spaces to avoid

